Capturing subdiffusive solute dynamics and predicting long timescale selectivity in nanoscale pores with time series modeling

### 2020-01-06 Ben_Manuscripts/stochastic_transport/Draft.tex
Incorporating MRS edits

%BJC5: wondering about replacing "Predicts long timescale behavior" with "predicts selectivity"
%MRS6: I would focus first on the outputs.  Not sure about the behavior/vs. selectivity.  Probably 
% selelctivity since it's more results oriented. ``of varying complexity'' is unneeded in the titel
%\title{Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics
%and Predicts Long Timescale Behavior in Nanoscale Pores.}
\title{Capturing subdiffusive solute dynamics and predicting long timescale selectivity in nanoscale pores
with time series modeling}
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

  \begin{abstract}
  Mathematically modeling complex transport phenomena at the molecular level 
  can be a powerful tool for identifying transport mechanisms and predicting
  macroscopic properties. We use two different stochastic time series models,
  parameterized from long molecular dynamics (MD) simulation trajectories of
  a cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
  membrane, in order to predict solute mean squared displacements (MSDs) 
  and solute flux,
  %MRS6: added
  and thus solute selectivity, 
  in macroscopic length pores. 
  %MRS6: tweak
  %With our first model, based on the 
  First, using
  anomalous diffusion theory, we show how solute dynamics can be modeled 
  as a fractional diffusion process subordinate to a continuous time random 
  walk. From the MD simulations, we parameterize the distribution of 
  dwell times, hop lengths between dwells and correlation between hops. We 
  explore 2 variations of the anomalous diffusion model. The first variation
  applies a single set of parameters to the solute displacements and the second
  applies 2 sets of parameters based on the solute's radial distance from the
  closest pore center. 
  %MRS6: tweak.

  Next, we generalize Markov state models,
  treating the configurational state of the system as a Markov process, each 
  %MRS6: tweak
  %of which has state dependent transport behavior. 
  state of which has separate transport properties
  For each state and transition
  between states, we parameterize the distribution and temporal correlation 
  structure of positional fluctuations as a means of characterization and to 
  allow us to predict solute MSDs. We show that our models reasonably reproduce
  the MSDs calculated from MD simulations.

  Finally, we demonstrate how one can
  use our models 
  %in order to calculate 
  to estimate
  flux of a 
  %given 
  solute across a 
  macroscopic-length pore and, based on those quantities, the membrane's selectivity
  towards each solute. Overall, this work helps to connect 
  % the relationship between
  microscopic chemically-dependent solute motions and macroscopic membrane performance.

@@

  Highly selective separations membranes are desirable in numerous applications. 
  The ability to efficiently separate ions from saline water sources using membranes 
  has been actively pursued for years in an effort to create potable water for people 
  in water-scarce regions.~\cite{werber_materials_2016} Even in relatively safe
  municipal water supplies, there is a need for membranes that can specifically separate
  potentially harmful organic micropollutants such as fertilizers, pesticides, pharmaceuticals
  and personal care products.~\cite{barbosa_occurrence_2016} In the materials industry,
  %BJC5: made more general. 
  there is a strong interest in creating breathable fabrics % barriers 
  % to chemical warfare agents
  which selectively allow passage of water vapor.~\cite{mondloch_destruction_2015}
%  The pace at which we achieve these or any other selective separation goals will be 
%  heavily influenced by the quality of insights gained by the modeling approaches above.

  Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that can be 
  cross-linked into mechanically strong and highly selective nanoporous membranes.~\cite{gin_polymerized_2008}
  They may provide a promising alternative to 
  % have the potential to disrupt
  conventional membrane separation techniques by being selective based not only on solute
  size and charge, but on solute chemical functionality as well.~\cite{dischinger_application_2017}
  One can tune the functionality of LLC monomers
  in order to enhance or weaken specific solute-membrane interactions.~\cite{dischinger_effect_2017}
  Tweaks.
  Two
  general types of LLC membranes 
  are 
  being actively developed.
  %in active development. 
  The inverted hexagonal, 
  H\textsubscript{II}, LLC phase has densely packed, uniform-sized pores on the order of 1 nm
  in size. A perfectly synthesized H\textsubscript{II} phase has an ideal geometry for high
  throughput separations, however aligning the microscopic hexagonal mesophases on a large 
  scale has shown limited success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
  Q\textsubscript{I}, phase LLCs share the uniform and nm-sized chemically complex pores of
  the H\textsubscript{II} phase but its geometry consists of a tortuous network of 3D 
  interconnected pores which do not require alignment.~\cite{carter_glycerol-based_2012} While 
  its pore structure may decrease a Q\textsubscript{I} membrane's permeability relative to the
  H\textsubscript{II} phase, it is considerably easier to synthesize at scale.

  Molecular modeling may make it possible to efficiently evaluate solute-specific separation
  membranes using the available chemical space of LLC monomers. To date, only a limited 
  subset of LLC monomers have been studied experimentally in membrane applications.
  %MRS6: should these references be contracted?
  \cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
  Even within this small subset, they have demonstrated selectivities that could not be
  explained beyond speculation and vague empirical correlations.~\cite{dischinger_application_2017}
  Atomistic molecular modeling can provide the resolution necessary to identify molecular 
  interactions that are key to separation mechanisms, allowing us to move beyond 
  Edisonian design approaches.

  In our previous work, we used molecular dynamics (MD) simulations to study the transport
  of 20 small polar molecules in an H\textsubscript{II} phase LLC membrane.~\cite{coscia_chemically_2019}
  %MRS6: sentence seems out of place here? True, but does it support the thesis here?
  The H\textsubscript{II} phase is a simpler geometry to model than the Q\textsubscript{I} phase.  
  In general, we observed subdiffusive transport behavior characterized by intermittent hops 
  separated by periods of entrapment. We identified three mechanisms responsible for the 
  solute trapping behavior: entanglement among monomer tails, hydrogen bonding with monomer
  head groups, and association with the monomer's sodium counter ions.

  %BJC4: Added next two paragraphs to help ease more into time series modeling
  So far, our molecular models have provided valuable qualitative mechanistic insight 
  with some quantitative support which already allows us to speculate about new LLC
  monomer designs
  %MRS6: breaking sentence.
  However, they would be of greater value to a 
  %wider audience 
  larger set of reseachers
  if we 
  could provide quantitative predictions of macroscopic observables such as solute 
  flux and selectivity. Due to the size of the types of systems we are studying (at least 62,000 atoms)
  it is prohibitively expensive and time-consuming to run simulations longer than 
  those performed for this work ($\sim$5 $\mu$s). 
  %MRS:deleting.
  %And 
  Even with the relatively large 
  size of our system, we only simulate 24 solute trajectories per unit cell in order
  to minimize solute-solute interactions. This results in relatively high uncertainties
  in observables such as mean squared displacement (MSD), preventing reliable long
  timescale predictions. We are in need of a way of studying the collective motion
  of a much larger set of solutes over much longer timescales.

@@

  %BJC4: Tried to make this paragraph connect to previous a little better
  Using a bottom-up modeling approach, we can parameterize single particle behavior
  by 
  %MRS6:
  extracting from 
  %reducing
  our MD simulations 
  %to observations of several key 
  properties
  of their trajectories
  that have the greatest influence on solute dynamics and then construct an ensemble 
  of characteristic single solute trajectories 
  with these properties
  useful for making long timescale
  predictions with computational ease and lower uncertainties. Fortunately, there 
  is an abundance of information encoded in the complex solute trajectories. Into a
  model, we can incorporate fluctuations and time-dependent correlations in solute
  position as well as the length of time solutes are trapped. We can add further
  detail by integrating our time series analysis with our knowledge of the primary
  trapping mechanisms as well as the solute's changing chemical environment within
  the heterogeneous membrane.

@@

  In this work, we use the output of our MD simulations to construct two classes of 
  mathematical models which aim to predict membrane performance while providing quantitative 
  mechanistic insights. The functional form of these models is driven by mechanistic 
  observations from our previous work and their inputs are parameterized using a 
  substantial amount of data generated by long ($\geq 5~\mu$s) MD simulations. 
  %MRS6: maybe rephrase the next - 'dive' is kind of casual?  Also, it seems more like the start of the next paragraph.
  The formulation
  of these models requires a dive into stochastically driven processes.

@@

  Where applicable, the sFBM model is an elegant way to characterize single 
  particle trajectories and in addition to providing an easy and efficient way to 
  simulate solute trajectories, can help uncover the underlying solute-membrane
  interactions which result in observed transport mechanisms. It can help 
  researchers formulate hypotheses to explain why a certain set of parameters is
  characteristic to a specific solute. 
  %MRS6: next sentence implies you used sFBM to uncover the mechanisms of the last paper, but that detail wasn't really there? 
  This is largely the approach we used to
  discover the three primary trapping mechanisms in our previous work.~\cite{coscia_chemically_2019}
  Once one has knowledge of the primary mechanisms leading to anomalous diffusion
  behavior, one may gain additional insight by formulating a state-based model.

@@

  % BJC4: new paragraph
  The goal of this work is not to definitively determine which modeling approach
  is better but to evaluate their performance independently because they both
  have potential value dependent on 
  %MRS:
  %one's research
  a give reseach study's
  goals. The anomalous subdiffusion
  approach provides a systematic way to compare the dynamical behavior of different
  solutes based solely on the time series of their center of mass positions. The process
  of choosing the correct anomalous subdiffusion provides its own mechanistic insight
  since it requires a thorough analysis of solute time series behavior. One can simulate
  different solutes, compare the fit model parameters and relate them back to 
  differences in solute size and chemical composition. The MSDDM characterizes 
  explicitly defined trapping mechanisms, providing a clear picture of solute behavior
  while in each trapped state as well as the equilibrium occupation of each trapping state.
  It is possible to use the two models in tandem, the anomalous diffusion model to
  identify mechanisms, and the MSDDM to characterize mechanisms.

@@

  Finally, we use both models in order to predict solute flux and selectivity in 
  pores of macroscopic length, thus achieving a better understanding
  of macroscopic properties on the basis of microscopic dynamics. We show that 
  anti-correlated solute hopping behavior severely reduces flux relative to 
  uncorrelated behavior. We use the relative solute fluxes to 
  %MRS6: tweak
  %calculate 
  estimate
  the 
  membrane's selectivity between all pairs of solutes and demonstrate that, when 
  solutes display different degrees of anti-correlated hopping behavior, selectivity
  becomes a function of pore length. With this improved understanding of 
  macroscopic behavior, we can begin to think more critically about how to design 
  membranes in order to selectively pass or reject specific solutes.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.4\textwidth}
  \centering
  \includegraphics[width=\textwidth]{NaGA3C11.pdf}
  \caption{}\label{fig:monomer_structure}
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=\textwidth]{membrane_profile.pdf}
  \caption{}\label{fig:membrane_profile}
  \end{subfigure}
  \caption{(a) The wedge-shaped liquid crystal monomer Na-GA3C11 will form the inverted
  hexagonal phase in the presence of water where the carboxylate head groups occupy the
  pore centers. (b) A cross-section of a periodically replicated atomistic unit cell 
  used for simulations in this study reveals the membrane's aqueous, hexagonally packed,
  straight and uniform sized pores. Water present in the 
  %MRS6: isn't distal tail redundant? 
  distal tail region is omitted 
  for clarity.}\label{fig:membrane_structure}
  \end{figure}

@@

  Solutes in this system 
  %MRS6: added
  very clearly 
  exhibit 
  subdiffusive behavior, a type of anomalous diffusion.
  During an anomalous diffusion process, the mean squared displacement (MSD)
  does not grow linearly with time, but instead it follows a power law of the form:
  %MRS6: do you need the subscript for $\alpha$? makes it harder to read. 
  \begin{equation} 
  \langle z^2(t) \rangle = K_{\alpha_d}t^{\alpha_d}
  \label{eqn:msd_form}
  \end{equation} 
  where $\alpha_d$ is the anomalous exponent and $K_{\alpha_d}$ is the generalized 
  diffusion coefficient. We only calculate MSD with respect to the solutes' center of
  mass $z$-coordinate, which is oriented along the pore axis. A value of $\alpha_d < 1$
  indicates a subdiffusive process, while values of $\alpha_d = 1$ and $\alpha_d > 1$ 
  are characteristic of Brownian and superdiffusive motion respectively.

  %MRS6: next paragraph could be clearer.  Maybe motivate at the beginning why the importance of time. vs. ensemble averated. It's sprung a sort of a surprise there's a difference 
  We analyzed the time-averaged MSD of the simulated trajectories by measuring
  all possible displacements over time lag $\tau$:
  \begin{equation}
  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
  \end{equation}
  where T is the length of the trajectory. Note that only the \textit{ensemble} MSD
  will reproduce the form of Equation~\ref{eqn:msd_form} in all cases. The ensemble
  MSD is given by:
  \begin{equation}
  \langle z^2(t) \rangle = \langle z(t) - z(0) \rangle^2
  \label{eqn:ensemble_msd}
  \end{equation} 
  In a pure CTRW, for example, the power law distribution of trapping times leads to
  weak ergodicity breaking. In this case, the time-averaged MSD is linear while the ensemble averaged
  MSD has the form of Equation~\ref{eqn:msd_form}.~\cite{meroz_toolbox_2015} With power
  law trapping behavior, the time between hops diverges so there is no characteristic
  measurement time scale of solute motion. In fact, as measurement time increases, the 
  average MSD of a CTRW tends to decrease, a phenomenon called aging, because trajectories 
  with trapping times on the order of the measurement time get incorporated into the 
  calculation.~\cite{bel_weak_2005} We chose to analyze just the time-averaged MSD 
  because, compared to the ensemble average, it is a more statistically robust measure
  of the average distance a solute travels over time. 
  %MRS6: does it correspond properly to the physical situation of entry into the pore of new particles at each unit time?
  Although theoretically possible, we do
  not use the MSD to calculate $\alpha_d$ because we can extract the same parameter 
  with higher precision using the dwell time distributions as described below.

@@

  \subsubsection{Subordinated Fractional L\'evy Motion}\label{method:sflm}
  %MRS6: maybe make it clearer that this is something you will be doing in the paper 
  Since we also want to account for the possibility that
  %If the 
  distribution of hops is not Gaussian, we can model them with the
  more general class of L\'evy stable distributions. For independent and identically
  distributed random variables, the generalized central limit theorem assures 
  convergence of the associated probability distribution function (PDF) to a 
  L\'evy stable PDF. \cite{klages_anomalous_2008} The characteristic equation which 
  describes the Fourier transform of a L\'evy stable PDF is:
  %MRS6: maybe use just $\alpha$ for the general subdiffusive case, and alpha_h here.   
  \begin{equation}
    p_{\alpha_h, \beta}(k;\mu,\sigma) =\exp\left[i\mu k - \sigma^{\alpha_h}|k|^{\alpha_h}\left(1 - i\beta\frac{k}{|k|}\omega(k, \alpha_h)\right)\right]
  \end{equation}
  where \\
  \[\omega(k, \alpha_h) = \begin{cases}
  	\tan{\frac{\pi \alpha_h}{2}} & \text{if}~\alpha_h \neq 1, 0 < \alpha_h < 2, \\
  	-\frac{2}{\pi}\ln |k| & \text{if}~\alpha_h = 1
  	 \end{cases}
  \]
  $\alpha_h$ is the index of stability or L\'evy index, $\beta$ is the skewness 
  parameter, $\mu$ is the shift parameter and $\sigma$ is a scale parameter. The most
  familiar case, and one of three that can be expressed in terms of elementary functions,
  is the Gaussian PDF ($\alpha_h$ = 2, $\beta$ = 0). We assume symmetric distributions
  centered about 0 implying that $\beta$ and $\mu$ are both 0.

@@

  We observe different dynamical behavior when solutes move while inside 
  the pore versus while in the tail region. This suggest two anomalous diffusion 
  models of varying complexity. We created a simple, single mode model with a single 
  set of parameters fit to solute trajectories.
%  $\alpha$, $\sigma$, $H$ and, when the truncated power law is used, $\lambda$ parameters
%  fit to solute trajectories.
  Our second, two mode model assigns a set of parameters to each of 2 modes based
  on the solute's radial location. Solutes in mode 1 are in the pore region, defined
  %MRS4: some justification on why 0.75 vs. any other cutoff.
  %BJC4: I justified sentence after next. 
  as less than 0.75 nm from any pore center. All else are in mode 2, the tail region. 
  We determined this cut-off by maximizing the difference in dynamical behavior as 
  described in our previous work.~\cite{coscia_chemically_2019} Unfortunately, 
  there were not enough sufficiently long sequences of hops in each mode to reliably
  calculate a Hurst parameter for each mode so we used the Hurst parameter from the 
  single mode model for both modes of the two mode model.

@@

  %\subsection{Solute Flux}\label{method:mfpt}
  %MRS6: tweak to make more active
  \subsection{Estimating Solute Flux}\label{method:mfpt}

>>>>

%BJC5: wondering about replacing "Predicts long timescale behavior" with "predicts selectivity"
%MRS6: I would focus first on the outputs.  Not sure about the behavior/vs. selectivity.  Probably 
% selelctivity since it's more results oriented. ``of varying complexity'' is unneeded in the titel
%\title{Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics
%and Predicts Long Timescale Behavior in Nanoscale Pores.}
% BJC6: The only issue with selectivity is that I don't think it would include a timescale.
\title{Capturing subdiffusive solute dynamics and predicting long timescale selectivity in nanoscale pores
with time series modeling}
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

  \begin{abstract}

  Mathematically modeling complex transport phenomena at the molecular level 
  can be a powerful tool for identifying transport mechanisms and predicting
  macroscopic properties. We use two different stochastic time series models,
  parameterized from long molecular dynamics (MD) simulation trajectories of
  a cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
  membrane, in order to predict solute mean squared displacements (MSDs) 
  and solute flux, and thus solute selectivity, in macroscopic length pores. 
  First, using anomalous diffusion theory, we show how solute dynamics can be
  modeled as a fractional diffusion process subordinate to a continuous time 
  random walk. From the MD simulations, we parameterize the distribution of 
  dwell times, hop lengths between dwells and correlation between hops. We 
  explore 2 variations of the anomalous diffusion model. The first variation
  applies a single set of parameters to the solute displacements and the second
  applies 2 sets of parameters based on the solute's radial distance from the
  closest pore center. Next, we generalize Markov state models, treating the
  configurational state of the system as a Markov process, each
  of which has separate transport properties. For each state and transition
  between states, we parameterize the distribution and temporal correlation 
  structure of positional fluctuations as a means of characterization and to 
  allow us to predict solute MSDs. We show that our models reasonably reproduce
  the MSDs calculated from MD simulations. Finally, we demonstrate how one can
  use our models to estimate flux of a solute across a macroscopic-length pore
  and, based on those quantities, the membrane's selectivity towards each solute.
  Overall, this work helps to connect microscopic chemically-dependent solute 
  motions and macroscopic membrane performance.

@@

  Highly selective separations membranes are desirable in numerous applications. 
  The ability to efficiently separate ions from saline water sources using membranes 
  has been actively pursued for years in an effort to create potable water for people 
  in water-scarce regions.~\cite{werber_materials_2016} Even in relatively safe
  municipal water supplies, there is a need for membranes that can specifically separate
  potentially harmful organic micropollutants such as fertilizers, pesticides, pharmaceuticals
  and personal care products.~\cite{barbosa_occurrence_2016} In the materials industry,
  there is a strong interest in creating breathable fabrics which selectively allow 
  passage of water vapor.~\cite{mondloch_destruction_2015}
%  The pace at which we achieve these or any other selective separation goals will be 
%  heavily influenced by the quality of insights gained by the modeling approaches above.

  Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that can be 
  cross-linked into mechanically strong and highly selective nanoporous membranes.~\cite{gin_polymerized_2008}
  They may provide a promising alternative to conventional membrane separation techniques
  by being selective based not only on solute size and charge, but on solute chemical 
  functionality as well.~\cite{dischinger_application_2017} One can tune the functionality
  of LLC monomers in order to enhance or weaken specific solute-membrane interactions.~\cite{dischinger_effect_2017}
  Two general types of LLC membranes are being actively developed. The inverted hexagonal, 
  H\textsubscript{II}, LLC phase has densely packed, uniform-sized pores on the order of 1 nm
  in size. A perfectly synthesized H\textsubscript{II} phase has an ideal geometry for high
  throughput separations, however aligning the microscopic hexagonal mesophases on a large 
  scale has shown limited success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
  Q\textsubscript{I}, phase LLCs share the uniform and nm-sized chemically complex pores of
  the H\textsubscript{II} phase but its geometry consists of a tortuous network of 3D 
  interconnected pores which do not require alignment.~\cite{carter_glycerol-based_2012} While 
  its pore structure may decrease a Q\textsubscript{I} membrane's permeability relative to the
  H\textsubscript{II} phase, it is considerably easier to synthesize at scale.

  Molecular modeling may make it possible to efficiently evaluate solute-specific separation
  membranes using the available chemical space of LLC monomers. To date, only a limited 
  subset of LLC monomers have been studied experimentally in membrane applications.
  %MRS6: should these references be contracted?
  %BJC6: probably, will see if that gets fixed by journal latex template
  \cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
  Even within this small subset, they have demonstrated selectivities that could not be
  explained beyond speculation and vague empirical correlations.~\cite{dischinger_application_2017}
  Atomistic molecular modeling can provide the resolution necessary to identify molecular 
  interactions that are key to separation mechanisms, allowing us to move beyond 
  Edisonian design approaches.

  In our previous work, we used molecular dynamics (MD) simulations to study the transport
  of 20 small polar molecules in an H\textsubscript{II} phase LLC membrane.~\cite{coscia_chemically_2019}
  %MRS6: sentence seems out of place here? True, but does it support the thesis here?
  %BJC6: I said above how the QI phase is easier to synthesize, so I felt it necessary to 
  % quickly justify why we studied the HII phase. Reworded to make that clearer. I'm also open to
  % eliminating the sentence.
  We chose to study the H\textsubscript{II} phase because it is a simpler geometry to model than 
  the Q\textsubscript{I} phase.  
  In general, we observed subdiffusive transport behavior characterized by intermittent hops 
  separated by periods of entrapment. We identified three mechanisms responsible for the 
  solute trapping behavior: entanglement among monomer tails, hydrogen bonding with monomer
  head groups, and association with the monomer's sodium counter ions.

  %BJC4: Added next two paragraphs to help ease more into time series modeling
  So far, our molecular models have provided valuable qualitative mechanistic insight 
  with some quantitative support which already allows us to speculate about new LLC
  monomer designs. However, they would be of greater value to a larger set of 
  researchers if we could provide quantitative predictions of macroscopic observables
  such as solute flux and selectivity. Due to the size of the types of systems we are 
  studying (at least 62,000 atoms) it is prohibitively expensive and time-consuming to
  run simulations longer than those performed for this work ($\sim$5 $\mu$s). 
  Even with the relatively large size of our system, we only simulate 24 solute trajectories per unit cell in order
  to minimize solute-solute interactions. This results in relatively high uncertainties
  in observables such as mean squared displacement (MSD), preventing reliable long
  timescale predictions. We are in need of a way of studying the collective motion
  of a much larger set of solutes over much longer timescales.

@@

  %BJC4: Tried to make this paragraph connect to previous a little better
  Using a bottom-up modeling approach, we can parameterize single particle behavior
  by extracting their trajectories from MD simulations and studying the properties that
  have the greatest influence on solute dynamics. With this information, we can learn
  how to construct an ensemble of characteristic single solute trajectories with these
  properties which would be useful for making long timescale predictions with computational
  ease and lower uncertainties. Fortunately, there is an abundance of information encoded
  in the complex solute trajectories. Into a
  model, we can incorporate fluctuations and time-dependent correlations in solute
  position as well as the length of time solutes are trapped. We can add further
  detail by integrating our time series analysis with our knowledge of the primary
  trapping mechanisms as well as the solute's changing chemical environment within
  the heterogeneous membrane.

@@

  In this work, we use the output of our MD simulations to construct two classes of 
  mathematical models which aim to predict membrane performance while providing quantitative 
  mechanistic insights. The functional form of these models is driven by mechanistic 
  observations from our previous work and their inputs are parameterized using a 
  substantial amount of data generated by long ($\geq 5~\mu$s) MD simulations. 
  %MRS6: maybe rephrase the next - 'dive' is kind of casual?  Also, it seems more like the start of the next paragraph.
  %BJC6: I just got rid of the sentence. It doesn't really add anything
%  The formulation
%  of these models requires a dive into stochastically driven processes.

@@

  Where applicable, the sFBM model is an elegant way to characterize single 
  particle trajectories and in addition to providing an easy and efficient way to 
  simulate solute trajectories, can help uncover the underlying solute-membrane
  interactions which result in observed transport mechanisms. It can help 
  researchers formulate hypotheses to explain why a certain set of parameters is
  characteristic to a specific solute. Once one has knowledge of the primary 
  mechanisms leading to anomalous diffusion behavior, one may gain additional
  insight by formulating a state-based model.

@@

  % BJC4: new paragraph
  The goal of this work is not to definitively determine which modeling approach
  is better but to evaluate their performance independently because they both
  have potential value dependent on a given research study's goals. The anomalous subdiffusion
  approach provides a systematic way to compare the dynamical behavior of different
  solutes based solely on the time series of their center of mass positions. The process
  of choosing the correct anomalous subdiffusion provides its own mechanistic insight
  since it requires a thorough analysis of solute time series behavior. One can simulate
  different solutes, compare the fit model parameters and relate them back to 
  differences in solute size and chemical composition. The MSDDM characterizes 
  explicitly defined trapping mechanisms, providing a clear picture of solute behavior
  while in each trapped state as well as the equilibrium occupation of each trapping state.
  It is possible to use the two models in tandem, the anomalous diffusion model to
  identify mechanisms, and the MSDDM to characterize mechanisms.

@@

  Finally, we use both models in order to predict solute flux and selectivity in 
  pores of macroscopic length, thus achieving a better understanding
  of macroscopic properties on the basis of microscopic dynamics. We show that 
  anti-correlated solute hopping behavior severely reduces flux relative to 
  uncorrelated behavior. We use the relative solute fluxes to estimate the 
  membrane's selectivity between all pairs of solutes and demonstrate that, when 
  solutes display different degrees of anti-correlated hopping behavior, selectivity
  becomes a function of pore length. With this improved understanding of 
  macroscopic behavior, we can begin to think more critically about how to design 
  membranes in order to selectively pass or reject specific solutes.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.4\textwidth}
  \centering
  \includegraphics[width=\textwidth]{NaGA3C11.pdf}
  \caption{}\label{fig:monomer_structure}
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=\textwidth]{membrane_profile.pdf}
  \caption{}\label{fig:membrane_profile}
  \end{subfigure}
  \caption{(a) The wedge-shaped liquid crystal monomer Na-GA3C11 will form the inverted
  hexagonal phase in the presence of water where the carboxylate head groups occupy the
  pore centers. (b) A cross-section of a periodically replicated atomistic unit cell 
  used for simulations in this study reveals the membrane's aqueous, hexagonally packed,
  straight and uniform sized pores. Water present in the tail region is omitted 
  for clarity.}\label{fig:membrane_structure}
  \end{figure}

@@

  Solutes in this system very clearly exhibit subdiffusive behavior, a type of
  anomalous diffusion. During an anomalous diffusion process, the mean squared 
  displacement (MSD) does not grow linearly with time, but instead it follows 
  a power law of the form:
  %MRS6: do you need the subscript for $\alpha$? makes it harder to read. 
  \begin{equation} 
  \langle z^2(t) \rangle = K_{\alpha_d}t^{\alpha_d}
  \label{eqn:msd_form}
  \end{equation} 
  where $\alpha_d$ is the anomalous exponent and $K_{\alpha_d}$ is the generalized 
  diffusion coefficient. We only calculate MSD with respect to the solutes' center of
  mass $z$-coordinate, which is oriented along the pore axis. A value of $\alpha_d < 1$
  indicates a subdiffusive process, while values of $\alpha_d = 1$ and $\alpha_d > 1$ 
  are characteristic of Brownian and superdiffusive motion respectively.

  %MRS6: next paragraph could be clearer.  Maybe motivate at the beginning why the importance of time. vs. ensemble averated. It's sprung a sort of a surprise there's a difference 
  %BJC6: reorganized a little and broke into paragraphs meant to convey separate ideas.

  One can measure MSD in two ways. The time-averaged MSD measures all observed
  displacements over time lag $\tau$: 
  \begin{equation}
  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
  \end{equation}
  where T is the length of the trajectory. The ensemble averaged MSD measures
  displacements with respect to a particle's initial position:
  \begin{equation}
  \langle z^2(t) \rangle = \langle z(t) - z(0) \rangle^2
  \label{eqn:ensemble_msd}
  \end{equation}
  Fits to the \textit{ensemble} averaged MSD will always reproduce the form of 
  Equation~\ref{eqn:msd_form}.

  The time averaged and ensemble averaged MSDs will give identical results 
  unless a system displays non-ergodic behavior. For a pure CTRW, the power 
  law distribution of trapping times leads to weak ergodicity breaking.
  In this case, the time-averaged MSD is linear while the ensemble averaged
  MSD has the form of Equation~\ref{eqn:msd_form}.~\cite{meroz_toolbox_2015} With
  power law trapping behavior, the time between hops diverges so there is no 
  characteristic measurement time scale of solute motion. In fact, as measurement 
  time increases, the average MSD of a CTRW tends to decrease, a phenomenon called
  aging, because trajectories with trapping times on the order of the measurement 
  time get incorporated into the calculation.~\cite{bel_weak_2005}

  We chose to analyze just the time-averaged MSD because, compared to the ensemble
  average, it is a more statistically robust measure of the average distance a 
  solute travels over time. 
  % MRS6: does it correspond properly to the physical situation of entry into the 
  % pore of new particles at each unit time?
  % BJC6: no, but neither does ensemble
  Although theoretically possible, we do not use the ensemble averaged MSD to 
  calculate $\alpha_d$ because we can extract the same parameter with higher 
  precision using the dwell time distributions as described below.

%  Only the \textit{ensemble} averaged MSD will reproduce the form of 
%  Equation~\ref{eqn:msd_form} in all cases.
%  
%  We analyzed the time-averaged MSD of the simulated trajectories by measuring
%  all possible displacements over time lag $\tau$:
%  \begin{equation}
%  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
%  \end{equation}
%  where T is the length of the trajectory. Note that only the \textit{ensemble} MSD
%  will reproduce the form of Equation~\ref{eqn:msd_form} in all cases. The ensemble
%  MSD is given by:
%  \begin{equation}
%  \langle z^2(t) \rangle = \langle z(t) - z(0) \rangle^2
%  \label{eqn:ensemble_msd}
%  \end{equation} 
%  In a pure CTRW, for example, the power law distribution of trapping times leads to
%  weak ergodicity breaking. In this case, the time-averaged MSD is linear while the ensemble averaged
%  MSD has the form of Equation~\ref{eqn:msd_form}.~\cite{meroz_toolbox_2015} With power
%  law trapping behavior, the time between hops diverges so there is no characteristic
%  measurement time scale of solute motion. In fact, as measurement time increases, the 
%  average MSD of a CTRW tends to decrease, a phenomenon called aging, because trajectories 
%  with trapping times on the order of the measurement time get incorporated into the 
%  calculation.~\cite{bel_weak_2005} We chose to analyze just the time-averaged MSD 
%  because, compared to the ensemble average, it is a more statistically robust measure
%  of the average distance a solute travels over time. 
%  %MRS6: does it correspond properly to the physical situation of entry into the pore of new particles at each unit time?
%  Although theoretically possible, we do
%  not use the MSD to calculate $\alpha_d$ because we can extract the same parameter 
%  with higher precision using the dwell time distributions as described below.

@@

  \subsubsection{Subordinated Fractional L\'evy Motion}\label{method:sflm}

  Since we also want to account for the possibility that distribution of hops is 
  not Gaussian, we can model them with the more general class of L\'evy stable 
  distributions. For independent and identically distributed random variables, 
  the generalized central limit theorem assures convergence of the associated 
  probability distribution function (PDF) to a L\'evy stable PDF. \cite{klages_anomalous_2008}
  The characteristic equation which describes the Fourier transform of a L\'evy stable PDF is:
  %MRS6: maybe use just $\alpha$ for the general subdiffusive case, and alpha_h here.   
  \begin{equation}
    p_{\alpha_h, \beta}(k;\mu,\sigma) =\exp\left[i\mu k - \sigma^{\alpha_h}|k|^{\alpha_h}\left(1 - i\beta\frac{k}{|k|}\omega(k, \alpha_h)\right)\right]
  \end{equation}
  where \\
  \[\omega(k, \alpha_h) = \begin{cases}
  	\tan{\frac{\pi \alpha_h}{2}} & \text{if}~\alpha_h \neq 1, 0 < \alpha_h < 2, \\
  	-\frac{2}{\pi}\ln |k| & \text{if}~\alpha_h = 1
  	 \end{cases}
  \]
  $\alpha_h$ is the index of stability or L\'evy index, $\beta$ is the skewness 
  parameter, $\mu$ is the shift parameter and $\sigma$ is a scale parameter. The most
  familiar case, and one of three that can be expressed in terms of elementary functions,
  is the Gaussian PDF ($\alpha_h$ = 2, $\beta$ = 0). We assume symmetric distributions
  centered about 0 implying that $\beta$ and $\mu$ are both 0.

@@

  We observe different dynamical behavior when solutes move while inside 
  the pore versus while in the tail region. This suggest two anomalous diffusion 
  models of varying complexity. We created a simple, single mode model with a single 
  set of parameters fit to solute trajectories.
  Our second, two mode model assigns a set of parameters to each of 2 modes based
  on the solute's radial location. Solutes in mode 1 are in the pore region, defined
  %MRS4: some justification on why 0.75 vs. any other cutoff.
  %BJC4: I justified sentence after next. 
  as less than 0.75 nm from any pore center. All else are in mode 2, the tail region. 
  We determined this cut-off by maximizing the difference in dynamical behavior as 
  described in our previous work.~\cite{coscia_chemically_2019} Unfortunately, 
  there were not enough sufficiently long sequences of hops in each mode to reliably
  calculate a Hurst parameter for each mode so we used the Hurst parameter from the 
  single mode model for both modes of the two mode model.

@@

  \subsection{Estimating Solute Flux}\label{method:mfpt}
